---
title: "Instacart Recommender Lab"
output: html_notebook
---

```{r}
library("ggplot2")
library("recommenderlab")
```

# import datasets
```{r}
df_train <- read.csv("user_to_product_rating_train.csv")
head(df_train)
```

# This convert the datasets to binary
```{r}
ratings_matrix <- as(df_train[,c(1,2)], "binaryRatingMatrix")
ratings_matrix
```

# The following image shows sparsity of the matrix:
```{r}
image(ratings_matrix[1:100, 1:100], main = "Binary rating matrix")
```
# Selecting the most relevant data
```{r}
train_matrix <- ratings_matrix[rowCounts(ratings_matrix) >= 305, colCounts(ratings_matrix) >= 3500]
train_matrix
```

# plotting sparsity of the relevant data
```{r}
image(train_matrix[1:100, 1:100], main = "Binary rating matrix")
```
# Sparsity of the datasets
```{r}
(1-(103478/(990*583)))*100
```
```{r}
# this help us in determing the given parameter in evaluationScheme fuction
min(rowCounts(train_matrix)) # it used to determine given
```

# creating cross validation for the datasets
```{r}
eval_sets <- evaluationScheme(data = train_matrix, method = "cross-validation", k = 3, given = 12)
eval_sets
```

```{r}
getData(eval_sets, "train")
getData(eval_sets, "known")
getData(eval_sets, "unknown")
sapply(eval_sets@runsTrain, length)
```

```{r}
# model_to_evaluate <- "IBCF"
# model_parameters <- NULL
# eval_recommender <- Recommender(data = getData(eval_sets, "train"), method = model_to_evaluate, parameter = model_parameters)
# eval_recommender
```

```{r}
# recom <- predict(eval_recommender, getData(eval_sets, "known"), n=5 )
# recom
```
```{r}
# as(recom, "list")
```
```{r}
# items_to_recommend <- 10
# eval_prediction <- predict(object = eval_recommender, newdata = getData(eval_sets, "known"), n = items_to_recommend, type ="ratings")
# class(eval_prediction)
```

# Popular Model
```{r}
results <- evaluate(x = eval_sets, method = "POPULAR", type = "topNList", n=c(1,3,5,10,15,20))
results
```
# Popular Model Performance
```{r}
avg(results)
```
```{r}
columns_to_sum <- c("TP", "FP", "FN", "TN")
indices_summed <- Reduce("+", getConfusionMatrix(results))[, columns_to_sum]
head(indices_summed)
```

# AUC for Popular Model
```{r}
plot(results, annotate=TRUE)
```
# Precision and recall for Popular Model
```{r}
plot(results, "prec/rec", annotate=TRUE)
```

# Comparing Multiple Algorithms
```{r}
Algorithms <- list(
"Random Items" = list(name="RANDOM", param=NULL),
"Popular Items" = list(name="POPULAR", param=NULL),
"User-Based CF" = list(name="UBCF", param=list(nn=25, method="Jaccard")),
"Item-Based CF" = list(name="IBCF", param=list(k=30, method="Jaccard", alpha=0.5, normalize_sim_matrix=FALSE)),
"Re-recommends Items" = list(name="RERECOMMEND", param=list()),
"Alternating Least Squares" = list(name="ALS_implicit", param=list(lambda=0.1, alpha=10, n_factors=10, n_iterations=10)),
"Association Rules" = list(name="AR", param=list(support=0.1, confidence=0.8, maxlen=3))
)
```

```{r}
# rec_mod <- recommenderRegistry$get_entries(dataType = "binaryRatingMatrix")
# rec_mod
```
```{r}
# rec_mod$POPULAR_binaryRatingMatrix$parameters
```


```{r}
com_results <- evaluate(x = eval_sets, method = Algorithms, type = "topNList", n=c(1,3,5,10,15,20))
com_results
```

# Algorithms Accuracy Using Metrics
```{r}
avg(com_results)
```

# Algorithms Accuracy Using Plots
```{r}
plot(com_results, annotate=c(3,2,6,1), legend="topright")
title("ROC Curve")
```

```{r}
plot(com_results, "prec/rec", annotate=c(3,2,6,1), legend="bottomright")
title("Precision-Recall")
```
# Parameter tunning for UBCF
```{r}
vector_nn <- c(5, 10, 20, 30, 40, 50)

models_to_optimize <- lapply(vector_nn, function(k){list(name = "UBCF", param = list(method = "Jaccard", nn = k))})
names(models_to_optimize) <- paste0("UBCF_nn_", vector_nn)
```

```{r}
n_recommendations <- c(1, 5, seq(10, 100, 10))
list_results <- evaluate(x = eval_sets, method = models_to_optimize, type = "topNList", n= n_recommendations)
```
# UBCF Accuracy Using PLots
```{r}
plot(list_results, annotate = 5, legend = "topleft") 
title("ROC curve")
```

```{r}
plot(list_results, "prec/rec", annotate = 5, legend = "bottomleft") 
title("Precision - Recall")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
